A mixture of hidden Markov models to predict the lymphatic spread in head and neck cancer depending on primary tumor location

### 2024-10-17 manuscript.qmd
minor changes
extended

$$
P \left( \mathbf{D} \mid \boldsymbol{\theta} \right) = \prod_k^K P \left( \mathbf{X}=\boldsymbol{\xi}_k \mid \boldsymbol{\theta}, T_k \right)
$$ {#eq-likelihood-HMM}

In @eq-likelihood-HMM we compute the likelihood of observing patient the diagnosis of each patient $k$, i.e. t-stage $T_k$ and involvement $\xi_k$.

@@

- $\pi_m^{s_k}$ is the mixing coefficient for subsite $s_k$ (where patient $k$ has their tumor) and model $m$,
- $P(\mathbf{D}_k \mid \boldsymbol{\theta}_m)$ is the likelihood of patient $k$'s diagnosis, given that it was generated by model $m$,
- $\boldsymbol{\theta}_m$ represents the parameters of model $m$,
- $\epsilon_{k}^m$ is the latent variable that indicates patient $k$ was generated by model $m$.

>>>>

$$
P \left( \mathbf{D} \mid \boldsymbol{\theta} \right) = \prod_k^K P \left( \mathbf{X}_k=\boldsymbol{\xi}_i \mid \boldsymbol{\theta}, T_k \right)
$$ {#eq-likelihood-HMM}

In @eq-likelihood-HMM we compute the likelihood of observing patient the diagnosis of each patient $k$, i.e. t-stage $T_k$ and involvement  $\mathbf{X}_k=\boldsymbol{\xi}_i$.

@@

- $\pi_m^{s_k}$ is the mixing coefficient for subsite $s_k$ (where patient $k$ has their tumor) and model $m$,
- $P(\mathbf{D}_k \mid \boldsymbol{\theta}_m)$ is the likelihood of patient $k$'s diagnosis, i.e. The involvement state $\mathbf{X}_k = \boldsymbol{\xi}_i$ and t-stage $T_k$, given that it was generated by model $m$,
- $\boldsymbol{\theta}_m$ represents the parameters of model $m$,
- $\epsilon_{k}^m$ is the latent variable that indicates patient $k$ was generated by model $m$.
